r5r: Rapid Realistic Routing with R5 in R

### 2020-09-17 r-package/paper2020/paper2020.Rmd
updates paper references

---
title: 'r5r: Rapid Realistic Routing with R5 in R'
author: "   "
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette: default
  github_document: default
abstract: " write abstract"
urlcolor: blue
vignette: |
  %\VignetteIndexEntry{r5r-intro} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
bibliography: references.json
---

@@

Transport routing is the process of finding the alternative routes and costs 
that connect places on a given transport network. Routing often involves complex
mathematical algorithms and it is a fundamental step required for transport
accessibility analysis, fleet allocation and transport simulation and planning
more broadly. Despite the long-standing importance of routing analysis to the 
field, transport researchers and practitioners still frequently face practical 
challenges with this task. These challenges involve for example the monetary 
costs of licensed software, data availability issues for data hungry models, and
the long computation times to run multiple routing scenarios, particularly in 
large and complex multimodal transport networks. While there is a growing number
of open source routing models (ref: stplnr, otp, dodgr), most options available 
only return the fastest route option between a set of origins and destinations. 
This simple approach overlooks how often people's actual route choices deviate 
from shortest travel time paths due to imperfect information, monetary costs and
safety issues among other reasons (refs, 1 2 3).
Refs:
1 - https://tram.mcgill.ca/Research/Publications/Who_will_use_it.pdf
2 - https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0134322
3 - https://www.tandfonline.com/doi/abs/10.1080/13658816.2019.1605075

Test [@http://zotero.org/users/local/FtLgDWw9/items/8CHCA2S3]

This paper presents [r5r](https://ipeagit.github.io/r5r/), a new open source 
R package for rapid realistic routing on multimodal transport networks based on
the [Rapid Realistic Routing on Real-world and Reimagined networks (R<sup>5</sup>)](https://github.com/conveyal/r5). R<sup>5</sup> is a powerful 
next-generation routing engine written in Java and developed at Conveyal (ref 1-2)
to replace its predecessor OpenTripPlanner. The r5r package provides a simple 
and friendly interface to run R<sup>5</sup> locally from within R, what allows 
users to efficiently calculate travel time matrices or generate multiple route 
alternatives between origins and destinations using seamless parallel computing.
1 - https://repository.asu.edu/items/54162
2- https://www.jtlu.org/index.php/jtlu/article/view/1074

>>>>

---
title: 'r5r: Rapid Realistic Routing with R5 in R'
author: "   "
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette: default
  github_document: default
abstract: "write abstract"
urlcolor: blue
vignette: |
  %\VignetteIndexEntry{r5r-intro} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
bibliography: references.json
---

@@

Transport routing is the process of finding the alternative routes and costs 
that connect places on a given transport network. Routing often involves complex
mathematical algorithms and it is a fundamental step required for transport
accessibility analysis, fleet allocation and transport simulation and planning
more broadly. Despite the long-standing importance of routing analysis to the 
field, transport researchers and practitioners still frequently face practical 
challenges with this task. These challenges involve for example the monetary 
costs of licensed software, data availability issues for data hungry models, and
the long computation times to run multiple routing scenarios, particularly in 
large and complex multimodal transport networks. While there is a growing number
of open source routing models [@lovelace2019stplanr; @padgham2019dodgr], most
options available only return the fastest route option between a set of origins 
and destinations. This simple approach overlooks how often people's actual route 
choices deviate from shortest travel time paths due to imperfect information, 
monetary costs and safety issues among other reasons [@larsen2011travel;
@zhu2015people; @conway2019getting].

This paper presents [r5r](https://ipeagit.github.io/r5r/), a new open source 
R package for rapid realistic routing on multimodal transport networks based on
the [Rapid Realistic Routing on Real-world and Reimagined networks (R<sup>5</sup>)](https://github.com/conveyal/r5). 
R<sup>5</sup> is a powerful next-generation routing engine written in Java and
developed at Conveyal [@conway2017evidencebased; @conway2018accounting] to
replace its predecessor OpenTripPlanner. The r5r package provides a simple and
friendly interface to run R<sup>5</sup> locally from within R, what allows users
to efficiently calculate travel time matrices or generate multiple route 
alternatives between origins and destinations using seamless parallel computing.
